Decomposition-based Job-shop Scheduling with Constrained Clustering

### 2021-10-12 Artificial Intelligence and Machine Learning/PADL_conference/Paper_draft_v1.tex
start of introduction checked

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming}
\end{abstract}
%
%
%
\section{Introduction}
Scheduling is one of the most crucial problems in various industrial, transportation, or healthcare applications
%\todo{add 1-2 citations for each application}
 \cite{pezzella2008genetic,chaudhry2016research,nouiri2018effective,demirbilek2019dynamically,schoenfelder2020nurse,wang2019routing,janakbhai2021blockchain}.

These applications resulted in different definitions of scheduling problems, with Job-shop Scheduling Problem (JSP) being among the most popular ones.
In JSP, operations of given jobs must be scheduled on available machines in an optimal way wrt.\ some pre-defined criteria. The latter include, for instance, minimization of makespan, i.e., the completion time of the last job, or tardiness, i.e., the sum of delays for all jobs completed after their deadlines.

However, JSP is a NP-complete combinatorial optimization problem \cite{DBLP:journals/mor/GareyJS76,SOTSKOV1995237} for which no efficient algorithms are known. Therefore, searching for an optimal solution with modern approaches like Answer Set Programming (ASP), Mixed Integer Programming, or Constraint Programming \cite{meng2020mixed,el2020job,al2017job}
%\todo{cite at least 1 paper solving JSP with these methods} 
often takes too much computation time, even for small instances. Practical applications require solving JSP instances of vast scale with thousands of operations \cite{zhang2010hybrid}.
As a result, many researchers focused on the development of efficient algorithms for finding high-quality approximations of the optimal schedule, including dispatching rules and other heuristic approaches~\cite{blackstone1982state}, or stochastic optimization techniques \cite{DBLP:journals/informs/VaessensAL96,DBLP:journals/jim/CalisB15}.  
The main issue of these approaches is that they require manual parametrization for a particular scheduling problem, which is tedious and error-prone. For instance, heuristic approaches might require the development of new heuristics or their combinations. Similarly, default parameters of stochastic methods might result in a finding of mediocre schedules.    
As a result, much focus of the recent research lies on the automation of the parametrization using machine learning techniques~\cite{bengio2020machine}.

@@

\section{Problem Definition}
The Job-shop Scheduling Problem (JSP) is one of the well-known scheduling problems \cite{baker1974introduction,lenstra1979computational}. An instance of a JSP comprises a set $J = \{ J_1, J_2, \dots ,J_n \}$  of jobs and a set $M = \{ M_1, M_2, \dots ,M_m \}$ of Machines. Each job $J_i$ has a sequence $(O_{i,1}, O_{i,2}, \dots ,O_{i,m})$ of operations that must be processed in a predefined order. Each machine $M_i$ executes an operation of each job with a known and fixed processing time. The main objective of a JSP solver is to find a schedule that minimizes some criteria like makespan, i.e., the total completion time for all jobs.
In addition, JSP makes the following assumptions:
\begin{itemize}
	\item Once an operation starts, it must be completed without interruptions.
	\item Each job has no duplicated operations, i.e., visits a machine only once.
	\item A machine cannot perform more than one operation at a time.
	\item All machines are available at all times.
	\item Processing the jobs starts at time 0.
\end{itemize}

>>>>

\keywords{Job-shop Scheduling  Problem \and Constrained Clustering \and Time Windows \and Answer Set Programming}
\end{abstract}
%
%
%
\section{Introduction}
Scheduling is one of the most crucial problems in various industrial, transportation, or healthcare applications
%\todo{add 1-2 citations for each application}
 \cite{pezzella2008genetic,chaudhry2016research,nouiri2018effective,demirbilek2019dynamically,schoenfelder2020nurse,wang2019routing,janakbhai2021blockchain}. 
%
Such applications result in different scheduling problem definitions, with the Job-shop Scheduling Problem (JSP) \cite{taillard1993benchmarks} being one if not the most well-known variant.
In JSP, operations of given jobs must be scheduled on available machines in an optimal way wrt.\ some pre-defined criteria. The latter include, for instance, minimization of makespan, i.e., the latest completion time of any job, or tardiness, i.e., the sum of delays over all jobs completed after their deadlines.

However, JSP is an NP-complete combinatorial optimization problem \cite{DBLP:journals/mor/GareyJS76,SOTSKOV1995237} for which no efficient algorithms are known. Therefore, searching for an optimal solution with state-of-the-art solvers for Answer Set Programming (ASP), Mixed Integer Programming, or Constraint Programming \cite{meng2020mixed,coltep19a,el2020job,al2017job}
%\todo{cite at least 1 paper solving JSP with these methods} 
often takes too much computation time, even for seemingly small instances. Practical applications instead necessitate solving JSP instances of large scale with thousands of operations~\cite{zhang2010hybrid}.
As a result, much research work focuses on % the development of 
efficient methods for finding high-quality approximations of optimal schedules, including dispatching rules and other heuristic approaches~\cite{blackstone1982state} as well as stochastic optimization techniques \cite{DBLP:journals/informs/VaessensAL96,DBLP:journals/jim/CalisB15}.  
The main issue of these approaches is that they require manual parametrization for a particular scheduling problem, which is tedious and error-prone. For instance, adapting heuristic methods might involve the development of new dispatching rules or specific combinations of existing ones. Similarly, merely utilizing default parameters for stochastic techniques might lead to mediocre schedules.    
In view of these challenges, recent research interest lies on the automated parametrization of approximation methods using machine learning methodologies~\cite{bengio2020machine}.

@@

\section{Problem Definition}
The Job-shop Scheduling Problem (JSP) is one of the well-known scheduling problems \cite{baker1974introduction,lenstra1979computational,taillard1993benchmarks}. An instance of a JSP comprises a set $J = \{ J_1, J_2, \dots ,J_n \}$  of jobs and a set $M = \{ M_1, M_2, \dots ,M_m \}$ of Machines. Each job $J_i$ has a sequence $(O_{i,1}, O_{i,2}, \dots ,O_{i,m})$ of operations that must be processed in a predefined order. Each machine $M_i$ executes an operation of each job with a known and fixed processing time. The main objective of a JSP solver is to find a schedule that minimizes some criteria like makespan, i.e., the total completion time for all jobs.
In addition, JSP makes the following assumptions:
\begin{itemize}
	\item Once an operation starts, it must be completed without interruptions.
	\item Each job has no duplicated operations, i.e., visits a machine only once.
	\item A machine cannot perform more than one operation at a time.
	\item All machines are available at all times.
	\item Processing the jobs starts at time 0.
\end{itemize}
